Synthesizing Symmetric Lenses

### 2018-06-30 papers/SymmetricLenses/main.tex
edits in progress to section 2

\begin{figure}
  % https://tex.stackexchange.com/questions/168741/showing-two-listings-in-a-table-side-by-side
  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}[
stringstyle=\upshape\sffamily
]
Jane Doe: 35000
John Public: 37500
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingA}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}[
stringstyle=\upshape\sffamily
]
lastname,firstname,company
Doe,Jane,Healthcare Inc.
Public,John,Insurance Co.
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingB}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}
let salary = number | "UNSET"
let emp_salary = name . " " . name . ": " salary
let emp_salaries = "" | emp_salary . ("\n" emp_salary)*
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingC}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}
let company = (name . ("Co." | "Inc." | "Ltd.")) | "UNSET" in
let emp_row = name . "," . name "," company in
let header = "firstname,lastname,company" in
let emp_insurances = header . ("\n" . emp_row)*
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingD}{\box0}

  \centering
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{|>{\columncolor{lightyellow}}c|>{\columncolor{lightgreen}}c|}
      \hline
      company.mgmt & company.hr \\
      \hline
      \listingA & \listingB \\
      \hline
      \listingC & \listingD \\
      \hline
    \end{tabular}
  }
  \caption{Example files used by management and HR, and regular expressions
    describing the formats of these files.}
  \label{fig:minimized-representations}
\end{figure}

\afm{i commented out the previous version, because this one was quickly written
  up to give you something to work off. Feel free to delete it if it isnt
  helpful. } We motivate our problem with an extended example. In our
theoretical company, human resources and upper management both keep information
about employees. HR needs to know the names of the employees as well as their
insurance providers. Management needs to know the names of employees and their
salary. Two example files, and regular expressions describing the formats, are
shown in Figure~\ref{fig:minimized-representations}. These two files should be
synchronized: if management adds a new employee, ``Richard Roe: 32500'', a new
row should be added to HR's file, ``Roe,Richard,UNSET''. Furthermore, if HR
changes ``John Public'' to ``Jon Public'', that name change should be reflected
in both files. However, not all the data should be synchronized. The HR file
should not get altered due to salary changes, and the management file should not
get altered due to insurance company changes. While names should be matched
across the two formats, insurance company and salary information should be left
unmatched. Such a synchronization can be achieved with simple symmetric lenses.

>>>>

\begin{figure}
  % https://tex.stackexchange.com/questions/168741/showing-two-listings-in-a-table-side-by-side
  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}[
stringstyle=\upshape\sffamily
]
Jane Doe: 38000
John Public: 37500
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingA}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}[
stringstyle=\upshape\sffamily
]
Name,Company
Jane Doe,Healthcare Inc.
John Public,Insurance Co.
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingB}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}
let salary = number | "N/A"
let emp_salary = name . " " . name . ": " salary
let emp_salaries = "" | emp_salary . ("\n" emp_salary)*
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingC}{\box0}

  \setbox0=\hbox{%
    \begin{minipage}{3.5in}
\begin{lstlisting}
let company = (name . ("Co." | "Inc." | "Ltd.")) | "UNK" in
let emp_ins = name . " " . name "," company in
let header = "Name,Company" in
let emp_insurance = header . ("\n" . emp_ins)*
\end{lstlisting}
    \end{minipage}
  }
  \savestack{\listingD}{\box0}

  \centering
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{|>{\columncolor{lightyellow}}c|>{\columncolor{lightgreen}}c|}
      \hline
      \texttt{company.mgmt} data file & \texttt{company.hr} data file \\
      \hline
      \listingA & \listingB \\
      \hline
      \cellcolor{yellow}\texttt{company.mgmt} regular expression & 
      \cellcolor{green}\texttt{company.hr}  regular expression\\
      \hline
      \cellcolor{yellow}\listingC & \cellcolor{green}\listingD \\
      \hline
    \end{tabular}
  }
  \caption{Example data files and corresponding regular expressions
  used by management and HR, respectively, to represent employee salaries and health
  insurance companies.  
   \ksf{fix colors so regular expressions are just slightly darker
  shade than data file.}}  
  \label{fig:minimized-representations}
\end{figure}

In this section, we give an overview of simple symmetric lenses and
our corresponding synthesis algorithm using an example drawn from a
hypothetical U.S. company.  In this company, human resources and upper
management store information about employees in separate files:
Management records the names of employees and their salaries while
Human Resources (HR) stores the names of employees and their health
insurance providers.  Figure~\ref{fig:minimized-representations} show
two example files and regular expressions describing the formats.
The company wants to keep these two files synchronized:
if management adds a new employee, ``Chris Roe: 32500'', 
the corresponding entry ``Chris Roe, UNK'' should be added to HR's file.

Furthermore, if HR
changes ``John Public'' to ``Jon Public'', that name change should be reflected
in both files. However, not all the data should be synchronized. The HR file
should not get altered due to salary changes, and the management file should not
get altered due to insurance company changes. While names should be matched
across the two formats, insurance company and salary information should be left
unmatched. Such a synchronization can be achieved with simple symmetric lenses.
